### 2016-07-22 syntax.tex
rewriting/fleshing out syntax section

The so-called ``garbled Bloom filter'' due to Dong, Chen and Wen~\cite{xxx}, which stores xor-shares of bitstring~$x \in S$ at positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array, can be captured by letting~$\Sigma=\bits^L$ for a specified integer~$L>0$.  Similarly, one can capture the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$. \tsnote{Check this, I forget the exact details now.}

>>>>

A Bloom filter with secret hash functions is captured by appending to~$M$ appropriate encodings of $h_1,h_2,\ldots,h_k$, and setting $\aux=\emptystring$.  Related constructions that use a secret key~$K$, but not for hashing are captured in analogous ways.

The so-called ``garbled Bloom filter'' due to Dong, Chen and Wen~\cite{xxx}, which stores xor-shares of bitstring~$x \in S$ at positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array, falls within our syntax by letting~$\Sigma=\bits^L$ for a specified integer~$L>0$.  Similarly the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$. \tsnote{Check this, I forget the exact details now.}
